---
title: "Homework3"
author: "seongbin AN"
date: '2020 9 23 '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## SOL0
Datacheck

```{r cars}
library(tidyverse)
library(ggplot2)
library(forecast)
library(seasonal)
library(aTSA)
library(timsac)
X<-read.csv("C://Users//stat//Desktop//학교//2-2//시계열//loadregr.csv")
dim(X)
head(X)
X_ts<-ts(X$MKw, start=c(1970,5),end=c(1979,12), frequency=12)
```

## SOL1
# Draw time series plot

```{r 1}
X_ts %>% autoplot() +
  ggtitle("Time series plot")
```
## SOL2
# Fit decomposition model and draw a plot with the original data, seasonally adjusted, trend-cycle component all together.

I make stationary test to choose best decomposition way

Classical decomposition(additive)
```{r 2-1}
dd1=decompose(X_ts,type="additive")
tseries::kpss.test(dd1$random,null="Level")
tsdisplay(dd1$random, main="residual")
```
Classical decomposition(multiplicative)
```{r 2-2}
dd2=decompose(X_ts,type="multiplicative")
tseries::kpss.test(dd2$random,null="Level")
tsdisplay(dd2$random, main="residual")
```
SEATS decomposition
```{r 2-3}
dd3<-seas(X_ts)
names(dd3)
dd3_r<-remainder(dd3)
tseries::kpss.test(dd3_r,null="Level")
tsdisplay(dd3_r, main="remainder")
```
X11 decomposition
```{r 2-4}
X_ts %>% seas(x11="") ->dd4
dd4_r=remainder(dd4)
tseries::kpss.test(dd4_r,null="Level")
tsdisplay(dd4_r, main="remainder")
```
STL decomposition
```{r 2-5}
dd5<-stl(X_ts,'periodic')
dd5_r=remainder(dd5)
tseries::kpss.test(dd5_r,null="Level")
tsdisplay(dd5_r, main="remainder")
```

Based on residual ACF&PACF plot and stationary test, 
X11 decomposition is being used


A plot with the original data, seasonally adjusted, trend-cycle component all together
```{r 2-plot}
X_ts %>% seas(x11="") ->fit
autoplot(X_ts, series="Data")+
  autolayer(trendcycle(fit),series="Trend") +
  autolayer(seasadj(fit),series="Seasonally Adjusted") +
  xlab("Time") + ylab("New orders index")+
  ggtitle("The monthly peak load for electricity Iowa") +
  scale_color_manual(values=c("gray","blue","red"),breaks=c("Data","Seasonally Adjusted","Trend"))

```

## SOL3
#  Draw sub-series seasonal effect graph in each month.
```{r 3}
fit %>% seasonal() %>% ggsubseriesplot()+ylab("Seasonal")
```
This graph shows shape of seasonal effect of each month
(Blue line is constant seasonal effect of each month)



## SoL4
#  Draw a polar seasonal plot.
```{r 4}
ggseasonplot(X_ts,polar=TRUE)+
  ggtitle("Ploar Seasonal plot")
```

























