---
title: "Modul_1"
author: "seongbin"
date: '2020 9 14 '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Modul-1 Time Series practice

There are five time series data sets. The first data set (dd1) is a random variation ti,e series

```{r dd1}
#dd1

dd1=matrix(c(1342,1442,1252,1343,1425,1362,1456,1272,1243,1359,1412,1253,1201,1478,1322,1406,1254,1289,1497,1208))
dd1.ts=ts(data=dd1, start =c(2006,1),frequency=4)
dd1.ts
plot(dd1.ts, mai ='Random variation Time Series')

```


The secind data set (dd2) is a seasonal variation time series
```{r dd2}
#dd2
dd2 = matrix(c(1142,1242,1452,1543,1125,1262,1456,1572,1143,1259,1462,1553,1121,1258,1472,1546,1154,1249,1477,1548))
dd2.ts=ts(data=dd2, start=c(2006,1),frequency=4)
dd2.ts
plot(dd2.ts, mai ="Seasonal variation Time Series")
```

##Stationary
Let's generate a white noise series
```{r WN}
WN <-runif(100, min =-0.5, max=0.5)
WN.ts<-ts(data=WN, start=c(1,1),frequency=1)
plot(WN.ts,mai="White noise")
abline(h=0)
```

The ACF and PACf plot show that the generated WN.ts is stationary
```{r stationary}
acf(WN.ts,main="ACF")
pacf(WN.ts,main="PACF")
```





Testing if WN.ts is satisfying "stationary"
```{r stationary-test}
tseries::kpss.test(WN.ts,null="Level")
```

##Non-stationary 

Let's generate a random walk series, , which is not-statioinary
```{r RW}
at<-runif(100, min=-0.5,max=0.5)
yt<-runif(100, min=-0.5,max=0.5)
for(i in 2:100){yt[i]=yt[i-1]+at[i]}

yt.ts<-ts(data=yt)
plot(yt.ts, mai = "Random walk")
abline(h=0)
```
The ACF and PACF plot show that generated random walk process(yt.ts) is not atationary

```{r non-stationary}
acf(yt.ts,main="ACF")
pacf(yt.ts,main="PACF")
```

KPSS test for stationary


```{r nonstationary-test}
tseries::kpss.test(yt.ts, null="Level")
tseries::kpss.test(yt.ts, null="Trend")

#추세를 제외하니 stationary를 가진다
```





































